---
title: "Untitled"
author: "JJayes"
date: '2022-05-23'
output: html_document
---
```{r}
library(tidyverse)
library(here)
library(magick)

```


Process::

Read in the PDF files. Convert them to images. 


```{r}
folder <- "pdfs"
fname <- "hh_1900_stockholm.pdf"

convert_to_jpeg <- function(folder, fname) {
  fstub <- str_remove(fname, ".pdf")

  pdf <- image_read_pdf(here(folder, fname))

  jpeg <- image_convert(pdf, format = "jpeg")

  n_pages <- length(jpeg)

  pages <- 1:n_pages

  make_image <- function(page) {
    message("Writing image ", page)

    filename <- str_c(here("jpegs_hh", fstub), "_", page, ".jpeg")

    jpeg[page] %>% image_write(filename, quality = 100)
  }
  
  walk(pages, make_image)
}

convert_to_jpeg(folder, fname)

```

Function to stick country_names to column names

```{r}

column_names <- function(countries) {
  year <- tibble(colnames = "year")
  
  metrics <- c("_B", "_D", "_M")
  
  tbl <- expand_grid(countries, metrics) %>%
    mutate(colnames = str_c(countries, metrics)) %>%
    select(colnames)

  year %>%
    bind_rows(tbl) %>%
    pull(colnames)
}
```

Function to process the data

```{r}
process_data <- function(path, countries) {
  df <- read.csv(here::here(path), sep = ";", skip = 2)

  df <- df %>%
    as_tibble() %>%
    mutate(across(where(is.character), parse_number)) %>%
    select(!where(is.logical))

  colnames(df) <- column_names(countries)

  df <- df %>%
    pivot_longer(-year) %>%
    separate(name, into = c("country", "var"), sep = "_") %>%
    filter(!is.na(value))
  
  min_year <- df %>% arrange(year) %>% slice(1) %>% pull(year)
  
  path_out <- str_c("mitchell", "_", min_year, "_", countries %>% paste0(collapse = "_"), ".rds")

  df %>% write_rds(here::here("data_out", path_out))
}
```


### Page 1

```{r}
path <- "jpegs/Mitchell-demographic-rates_6.jpg_tab.csv"

countries <- c("Finland", "Norway", "Sweden")

process_data("jpegs/Mitchell-demographic-rates_1.jpg_tab.csv", c("Finland", "Norway", "Sweden"))

```

### Page 2


```{r}
process_data("jpegs/Mitchell-demographic-rates_2.jpg_tab.csv", c("Austria", "Belgium", "Denmark", "Finland"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_2.jpg_tab.csv", c("Austria", "Belgium", "Denmark", "Finland"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_3.jpg_tab.csv", c("Austria", "Belgium", "Bulgaria", "Denmark"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_4.jpg_tab.csv", c("Serbia", "Spain", "Sweden"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_5.jpg_tab.csv", c("Czechoslovakia", "Denmark", "Finland", "France"))

```


```{r}
process_data("jpegs/Mitchell-demographic-rates_6.jpg_tab.csv", c("Russia", "Serbia", "Spain", "Sweden"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_7.jpg_tab.csv", c("Czechoslovakia", "Denmark", "Finland", "France"))

```


```{r}
process_data("jpegs/Mitchell-demographic-rates_8.jpg_tab.csv", c("Norway", "Poland", "Portugal", "Romania"))

```

```{r}
process_data("jpegs/Mitchell-demographic-rates_8.jpg_tab.csv", c("Norway", "Poland", "Portugal", "Romania"))

```


```{r}
process_data("jpegs/Mitchell-demographic-rates_9.jpg_tab.csv", c("Russia", "Spain", "Sweden"))

```


```{r}
files <- list.files(path = here::here("data_out"), pattern = ".*.rds") %>% 
    str_c("data_out/", .)

df <- map(files, read_rds) %>% 
    bind_rows()

df <- df %>% 
    filter(country %in% c("Norway", "Sweden", "Denmark"))

# df %>% write_rds("data_out/mitchell_collected.rds")
```


## Stockholms hyrlista

```{r}
df <- read.csv(here::here("dewarped", "IMG_1571_thresh.png_tab.csv"), skip = 2, sep = ";")

df %>% as_tibble()


```

### Joberg day wages

```{r}
# page 3
df <- read.csv(here::here("jpegs", "Jöberg_1972_day_wages_3.jpg_tab.csv"), skip = 2, sep = ";")

df_3 <- df %>% as_tibble() %>% 
    janitor::clean_names() %>% 
    select(year, average_price_1, cv_1) %>% 
    # fixing error
    mutate(year = case_when(
        year == 1809 ~ 1909,
        TRUE ~ year
    ))

# page 2
df <- read.csv(here::here("jpegs", "Jöberg_1972_day_wages_2.jpg_tab.csv"), skip = 2, sep = ";")

df_2 <- df %>%
  as_tibble() %>%
  janitor::clean_names() %>%
  mutate(year = parse_number(year)) %>%
  arrange(year) %>%
  select(year, average_price_1, cv_1) %>%
  mutate(across(where(is.character), parse_number)) %>%
  filter(!is.na(average_price_1))

# page 1
df <- read.csv(here::here("jpegs", "Jöberg_1972_day_wages_1.jpg_tab.csv"), skip = 2, sep = ";")

df_1 <- df %>%
  as_tibble() %>%
  janitor::clean_names() %>%
  select(year, average_price_1, cv_1) %>%
  mutate(across(where(is.character), parse_number)) %>%
  filter(!is.na(average_price_1)) %>%
  mutate(year = case_when(
    year == 1891 ~ 1791,
    TRUE ~ year
  ))


df_wages <- df_1 %>% 
    bind_rows(df_2) %>% 
    bind_rows(df_3)

# df_wages %>% write_rds("data_out/Joberg_day_wages_sweden.rds")
```

## HH stockholm

page 1

```{r}
df <- read.csv(here::here("jpegs", "hh_1890_stockhom_1.jpg_tab.csv"), skip = 2, sep = ";")

df %>%
  as_tibble() %>%
  janitor::clean_names() %>% 
    select(!x) %>% 
    mutate(x_1 = str_c(x_1, x_2)) %>% 
    select(!x_2) %>% 
    mutate(across(where(is.numeric), as.character)) %>% 
    pivot_longer(-x_1) %>% 
    mutate(value_num = str_remove(value, "[:punct:]"),
           value_num = parse_number(value_num, locale = locale(decimal_mark = ","))) %>% view()

```

page 2

```{r}
df <- read.csv(here::here("jpegs", "hh_1890_stockhom_2.jpg_tab.csv"), skip = 2, sep = ";")

df %>%
  as_tibble() %>%
  janitor::clean_names() %>% 
    select(!x) %>% 
    mutate(across(where(is.numeric), as.character)) %>% 
    pivot_longer(-x1) %>% 
    mutate(value_num = str_remove(value, "[:punct:]"),
           value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
           name = parse_number(name)) %>% 
    select(!value) %>% 
    rename(col = name,
           value = value_num)
```

page 3

```{r}
df <- read.csv(here::here("jpegs", "hh_1890_stockhom_3.jpg_tab.csv"), skip = 2, sep = ";")

df %>%
  as_tibble() %>% view()
  janitor::clean_names() %>% 
    select(!x) %>% 
    mutate(across(where(is.numeric), as.character)) %>% 
    pivot_longer(-x1) %>% 
    mutate(value_num = str_remove(value, "[:punct:]"),
           value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
           name = parse_number(name)) %>% 
    select(!value) %>% 
    rename(col = name,
           value = value_num)
```




page 4

```{r}
df <- read.csv(here::here("jpegs", "hh_1890_stockhom_4.jpg_tab.csv"), skip = 2, sep = ";")

df %>%
  as_tibble() %>% view()
  janitor::clean_names() %>% 
    select(!x) %>% 
    mutate(across(where(is.numeric), as.character)) %>% 
    pivot_longer(-x1) %>% 
    mutate(value_num = str_remove(value, "[:punct:]"),
           value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
           name = parse_number(name)) %>% 
    select(!value) %>% 
    rename(col = name,
           value = value_num)
```

I need to work on some code that splits the text in each column logically if we get two in one.

```{r}
json <- jsonlite::fromJSON("jpegs/Mitchell-demographic-rates_1.jpeg_blocks.json")

listviewer::jsonedit(json)

json[["BlockType" == "CELL"]]

json$BlockType
```

# 1911

Function to read in tav

```{r}
read_tab <- function(number){
    read.csv(here::here("jpegs", glue::glue("hh_1911_stockholm_bigger_{number}.jpg_tab.csv")), skip = 2, sep = ";")
    
}
```

Function to process data

```{r}
process_tab <- function(tbl, second_col) {
  tbl %>%
    as_tibble() %>%
    janitor::clean_names() %>%
    select(!x) %>%
    mutate(across(where(is.numeric), as.character)) %>%
    pivot_longer(-second_col) %>%
    mutate(
      value_num = str_remove(value, "[:punct:]"),
      value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
      name = parse_number(name)
    ) %>%
    select(!value) %>%
    rename(
      col = name,
      value = value_num
    ) %>%
    rename(parish = 1)
}
```

page 1 of 1911

```{r}
number <- 1

df <- read_tab(number)

df <- process_tab(df, "x1")

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))
```

page 2 of 1911

```{r}
number <- 2

df <- read_tab(number)

df <- process_tab(df, "x1")

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))
```



page 3 of 1911

```{r}
number <- 3

df <- read_tab(number)

df <- process_tab(df, "x1")

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))
```





page 4 of 1911

```{r}
number <- 4

df <- read_tab(number)

df <- process_tab(df, "x1")

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))
```


page 5 of 1911 part 1

```{r}
number <- "5_1"

df <- read_tab(number)

df <- process_tab(df, "x1")

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))
```


page 5 of 1911 part 2

```{r}
number <- "5_2"
second_col <- "x_1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1911", glue::glue("hh_1911_{number}.rds")))

```


# 1865

Function to read in tab

```{r}
read_tab <- function(number){
    read.csv(here::here("jpegs_hh", glue::glue("hh_1865_stockholm_{number}.jpg_tab.csv")), skip = 2, sep = ";")
    
}
```

Function to process data

```{r}
process_tab <- function(tbl, second_col) {
  tbl %>%
    as_tibble() %>%
    janitor::clean_names() %>%
    select(!x) %>%
    mutate(across(where(is.numeric), as.character)) %>%
    pivot_longer(-second_col) %>%
    mutate(
      value_num = str_remove(value, "[:punct:]"),
      value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
      name = parse_number(name)
    ) %>%
    select(!value) %>%
    rename(
      col = name,
      value = value_num
    ) %>%
    rename(parish = 1)
}
```

page 1 of 1865

```{r}
number <- "1"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 2 of 1865

```{r}
number <- "2"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 3 of 1865

```{r}
number <- "3"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 4 of 1865

```{r}
number <- "4"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 5 of 1865

```{r}
number <- "5"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 6 of 1865

```{r}
number <- "6"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 7 of 1865

```{r}
number <- "7"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


page 8 of 1865

```{r}
number <- "8"
second_col <- "x1"

df <- read_tab(number)

df <- process_tab(df, second_col)

df %>% write_rds(here::here("1865", glue::glue("hh_1865_{number}.rds")))

```


# 1890

Function to read in tab

```{r}
read_tab <- function(number) {
  read.csv(here::here("jpegs_hh", glue::glue("hh_1890_stockholm_{number}.jpg_tab.csv")), skip = 2, sep = ";")
}
```

Function to process data

```{r}
process_tab <- function(tbl, second_col) {
  tbl %>%
    as_tibble() %>%
    janitor::clean_names() %>%
    select(!x) %>%
    mutate(across(where(is.numeric), as.character)) %>%
    pivot_longer(-second_col) %>%
    mutate(
      value_num = str_remove(value, "[:punct:]"),
      value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
      name = parse_number(name)
    ) %>%
    select(!value) %>%
    rename(
      col = name,
      value = value_num
    ) %>%
    rename(parish = 1)
}
```

page 1 of 1890

```{r}
number <- "1"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```

page 2 of 1890

```{r}
number <- "2"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```

page 3 of 1890

```{r}
number <- "3"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```

page 4 of 1890

```{r}
number <- "4"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```

page 5 of 1890
I need to fix this one...
```{r}
number <- "5"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```


page 6 of 1890

```{r}
number <- "6"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1890", glue::glue("hh_1890_{number}.rds")))
```

# 1900


Function to read in tab

```{r}
read_tab <- function(number) {
  read.csv(here::here("jpegs_hh", glue::glue("hh_1900_stockholm_{number}.jpg_tab.csv")), skip = 2, sep = ";")
}
```

Function to process data

```{r}
process_tab <- function(tbl, second_col) {
  tbl %>%
    as_tibble() %>%
    janitor::clean_names() %>%
    select(!x) %>%
    mutate(across(where(is.numeric), as.character)) %>%
    pivot_longer(-second_col) %>%
    mutate(
      value_num = str_remove(value, "[:punct:]"),
      value_num = parse_number(value_num, locale = locale(decimal_mark = ",")),
      name = parse_number(name)
    ) %>%
    select(!value) %>%
    rename(
      col = name,
      value = value_num
    ) %>%
    rename(parish = 1)
}
```

page 1 of 1900

```{r}
number <- "1"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1900", glue::glue("hh_1900_{number}.rds")))
```


page 2 of 1900

```{r}
number <- "2"
second_col <- "x_1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1900", glue::glue("hh_1900_{number}.rds")))
```


page 3 of 1900

```{r}
number <- "3"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1900", glue::glue("hh_1900_{number}.rds")))
```


page 4 of 1900

```{r}
number <- "4"
second_col <- "x_1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1900", glue::glue("hh_1900_{number}.rds")))
```


page 5 of 1900

```{r}
number <- "5_1"
second_col <- "x1"
df <- read_tab(number)
df <- process_tab(df, second_col)
df %>% write_rds(here::here("1900", glue::glue("hh_1900_{number}.rds")))
```




